On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-08-16 manuscripts/PNAS/chazthm_pnas.tex
k to 2k in f(A)

Another extension of Thm.~\ref{DeterministicUniquenessTheorem} arises from the following analytic characterization of the spark condition.  Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$. When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
\begin{align*}
f(\mathbf{A}) := \prod_{S \in {[m] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \mathbf{A}_{S',S})^2,
\end{align*}
%
where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.   We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether a given matrix $\mathbf{A}$ satisfies the spark condition \cite{tillmann2014computational}.

@@

>>>>

Another extension of Thm.~\ref{DeterministicUniquenessTheorem} arises from the following analytic characterization of the spark condition.  Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$. When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
\begin{align*}
f(\mathbf{A}) := \prod_{S \in {[m] \choose 2k}} \sum_{S' \in {[n] \choose 2k}} (\det \mathbf{A}_{S',S})^2,
\end{align*}
%
where for any $S' \in {[n] \choose 2k}$ and $S \in {[m] \choose 2k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.   We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether a given matrix $\mathbf{A}$ satisfies the spark condition \cite{tillmann2014computational}.

@@

%Another extension of Thm.~\ref{DeterministicUniquenessTheorem} arises from the following analytic characterization of the spark condition.  Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$. When real numbers are substituted for $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
%\begin{align*}
%f(\mathbf{A}) := \prod_{S \in {[m] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \mathbf{A}_{S',S})^2,
%\end{align*}
%
%where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.   We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether a given matrix $\mathbf{A}$ satisfies the spark condition \cite{tillmann2014computational}.

%Since $f$ is analytic, having a single substitution of a real matrix $\mathbf{A}$ with $f(\mathbf{A}) \neq 0$ necessarily implies that the zeroes of $f$ form a set of measure zero. Fortunately, such a matrix $\mathbf{A}$ is easily constructed by adding rows of zeroes to any $\min(2k,m) \times m$ Vandermonde matrix as described above (so that each term in the product above for $f$ is nonzero). Hence, almost every $n \times m$ matrix with $n \geq \min(2k,m)$ satisfies \eqref{SparkCondition}.
